Resurgence of the Airy function

### 2022-03-27 airy-resurgence.tex
Rewrite Borel regularity argument using slight functions

\usepackage{url}
\usepackage[hmargin=1.5in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{xcolor} %% for revisions

@@

\begin{document}
\maketitle
\section{The Laplace transform}
\subsection{Analytic version}
\subsubsection{Regularity and decay properties}\label{reg-decay}
Take two copies $\R$ and $\hat{\R}$ of the real line, with standard coordinates $z$ and $\zeta$ respectively. The Laplace transform in $\zeta$ turns a function $\hat{\varphi}$ on $\hat{\R}_{\zeta > 0}$ into a function $\laplace_\zeta \hat{\varphi}$ on $\R_{z > 0}$, defined by the integral
\[ \laplace_\zeta \hat{\varphi} = \int_0^\infty e^{-z \zeta}\,\hat{\varphi}\;d\zeta. \]
For $a \in [0, \infty]$, recall that recall that $O_{\zeta \to a}(g)$ is the space of functions $\varphi$ on $\hat{\R}_{\zeta > 0}$ with $|\varphi| \lesssim g$ in some neighborhood of $a$. A function is {\em subexponential} if it's in $O_{\zeta \to \infty}(e^{c\zeta})$ for all $c > 0$. Let $\mathcal{E}_\zeta$ be the space of subexponential functions on $\hat{\R}_{\zeta > 0}$ which are $L^1$ both locally and around $\zeta = 0$. If $\hat{\varphi}$ is in $\mathcal{E}_\zeta$, then $\varphi = \laplace_\zeta \hat{\varphi}$ is well-defined, and it extends to a holomorphic function on the right half-plane $\C_{\operatorname{Re}(z) > 0}$~\cite[\S 5.6]{diverg-resurg-i}. If $\hat{\varphi}$ is in $O_{\zeta \to 0}(1)$, then $\varphi$ is in $O_{z \to \infty}(z^{-1})$~\cite[equation~1.8]{laplace-tfm}.\footnote{The argument cited still works in our generality. For holomorphic $\hat{\varphi}$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textbf{(Sternin \& Shatalov)}.} More generally, if $\hat{\varphi}$ is in $O_{\zeta \to 0}(\zeta^{\alpha})$, with $\alpha > -1$, then $\varphi$ is in $O_{z \to \infty}\big(z^{-(\alpha + 1)}\big)$.
\subsubsection{Action on differential and integral operators}\label{L-diff-op}
When $\hat{\varphi} \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
\begin{equation}\label{id:L-mult}
\laplace_\zeta (\zeta^n \hat{\varphi}) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \hat{\varphi}.
\end{equation}
for all integers $n \ge 0$. You can also use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \hat{\varphi} \in \mathcal{E}_\zeta$ and
\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \hat{\varphi} = z^{-\lambda} \laplace_{\zeta, a} \hat{\varphi} \]
for all $\lambda \in (0, \infty)$.

@@

Now we have the results of Section~\ref{L-diff-op} for all functions in $\mathcal{E}_\zeta + \mathcal{P}_\zeta$. Identity~\ref{id:L-diff} is particularly simple when $\hat{\varphi}$ has a {\em fractional power singularity} at $\zeta = 0$. By this, I mean that $\hat{\varphi}$ can be written as $\hat{\varphi}_\text{frac} + \hat{\varphi}_\text{reg}$, where $\hat{\varphi}_\text{frac} \in \mathcal{P}_\zeta$ has only non-integer exponents, and the zeroth through $(n-1)$st derivatives of $\hat{\varphi}_\text{reg} \in \mathcal{E}_\zeta$ vanish at zero. Under this condition, all the initial value terms in the identity vanish, leaving
\[ \laplace_\zeta \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} = z^n \laplace_\zeta \hat{\varphi}. \]
\color{black}
\subsection{Change of coordinates}
Define a new coordinate $\zeta_a$ on $\hat{\R}$ so that $\zeta = a + \zeta_a$. From the calculation \textbf{[using variable starting point notation]}
\begin{align*}
\laplace_{\zeta, a} \hat{\varphi} & = \int_a^\infty e^{-z \zeta}\,\hat{\varphi}\;d\zeta \\
& = \int_0^\infty e^{-z(a + \zeta_a)}\,\hat{\varphi}\;d\zeta_a \\
& = e^{-az} \int_0^\infty e^{-z\zeta_a}\,\hat{\varphi}\;d\zeta_a \\
& = e^{-az} \laplace_{\zeta_a, 0} \hat{\varphi},
\end{align*}
we learn that
\[ \laplace_{\zeta_a, 0} \hat{\varphi} = e^{az} \laplace_{\zeta, a} \hat{\varphi}. \]

Define new coordinates $x$ and $\xi$ on $\R$ and $\hat{\R}$, respectively, so that $\zeta = b\xi$ and $z\,d\zeta = x\,d\xi$. Explicitly, $z = b^{-1}x$. From the calculation
\begin{align*}
\laplace_\zeta \hat{\varphi} & = \int_0^\infty e^{-z \zeta}\,\hat{\varphi}\;d\zeta \\
& = \int_0^\infty e^{-x\xi}\,\hat{\varphi}\;b\,d\xi \\
& = b \laplace_\xi \hat{\varphi},
\end{align*}
we learn that
\[ \laplace_\xi \hat{\varphi} = b^{-1} \laplace_\zeta \hat{\varphi}. \]
\section{Shifting integro-differential equations}
Consider holomorphic functions on a simply connected open set that touches but doesn't contain $\zeta = 0$. A function is {\em regular} at $\zeta = 0$ if it extends holomorphically over that point. We'll say a function is {\em slight} at $\zeta = 0$ if it can be written as
\begin{equation}\label{eqn:slight-defn}
\zeta^{\alpha_1} f_1 + \ldots + \zeta^{\alpha_r} f_r + g
\end{equation}
where $f_1, \ldots, f_r$ are regular, $\alpha_1, \ldots, \alpha_r \in \R \smallsetminus \Z$, and $g, g', g'', \ldots$ go to zero at $\zeta = 0$.

Locally integrable slight functions play a special role in Laplace transform methods for linear differential equations. This is because differential equations in the spatial domain arise most naturally from integral equations in the frequency domain, but we'd like to work with differential equations in the frequency domain too. In the space of locally integrable slight functions, differential and integral equations enjoy their simplest equivalence.
\begin{prop}\label{prop:shift}
When $\psi$ is slight and locally integrable at $\zeta = 0$,
\[ \left[ \sum_{k = 0}^n \big(\tfrac{\partial}{\partial \zeta}\big)^k \circ h_k + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
if and only if
\[ \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k + \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
where $h_n, \ldots, h_{-m}$ are regular functions.
\end{prop}
To prove this result, we'll need a little background.

@@

Multiplication by a regular function and differentiation with respect to $\zeta$ both preserve the space of slight functions. Integration from $\zeta = 0$ preserves the space of locally integrable slight functions. Thus, in general, integro-differential operators with regular coefficients send locally integrable slight functions to slight functions. Each basic operation has a simple effect on a slight function's order. Multiplication by $\zeta^n f$, where $f$ is regular and non-vanishing at $\zeta = 0$, adds $n$ to the order. Differentiation and integration add $-1$ and $1$, respectively.
\begin{proof}[Proof of Proposition~\ref{prop:shift}]
The reverse implication holds without any special condition on $\psi$, because $\tfrac{\partial}{\partial \zeta}\;\fracderiv{-1}{\zeta}{0}$ acts as the identity on all differentiable functions.

@@

Integrating both sides of equation~\ref{eqn:diff-int-split}, we get
\[ \fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}\;\phi = -\left[ \fracderiv{-1}{\zeta}{0} \circ h_0 + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k-1} \right] \psi. \]
Since $\fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}$ acts as the identity on functions that vanish at $\zeta = 0$, this simplifies to
\[ \phi = -\left[ \sum_{k = 0}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k-1} \right] \psi, \]
which rearranges to the second equation in the statement.
\end{proof}

@@

The method we'll demonstrate in Section~\ref{spatial} works for any differential equation
\[ \left[ z P\big(\tfrac{\partial}{\partial z}\big) + Q\big(\tfrac{\partial}{\partial z}\big) + R(z^{-1}) \right] \varphi = 0, \]
where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function with no constant term. We'll recast equation~\ref{eqn:mod-bessel} in this form:
\begin{equation}\label{eqn:std-mod-bessel}
\left[z \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-1} \right] \varphi = 0.
\end{equation}

\color{violet}
As we'll see in Section~\ref{asymp}, $K$ is in $O_{z \to \infty}(e^{-z})$. It'll be helpful to pull out the exponential decay factor and work instead with the function $\kappa$ defined by $K = e^{-z} \kappa$. Saying that $K$ satisfies equation~\ref{eqn:mod-bessel} is equivalent to saying that $\kappa$ satisfies the equation
\begin{equation}\label{eqn:shifted-mod-bessel}
\left[z^2 \big(\tfrac{\partial}{\partial z} + 1\big)^2 + z \big(\tfrac{\partial}{\partial z} + 1\big) - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] \varphi = 0.

@@

\subsection{Guessing solutions}
\subsection{Asymptotic analysis}
Equation~\ref{eqn:mod-bessel} has a regular singularity at $0$ and an irregular singularity at $\infty$. From the general theory of such equations, we know that the space of trans-series solutions has a basis of the form
\[ \{e^{-\alpha z} z^{\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \} \]
where the $\series{W}_\alpha$ are formal power series in $z^{-1}$ with no constant term. From equations 10.40.2 and 10.17.1 of \cite{dlmf}, we learn that $K \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{1/2}\,\series{W}_1$, with
\begin{equation}\label{bessel-asymp}
\series{W}_1 = z^{-1} - \frac{(\tfrac{1}{6})_1 (\tfrac{5}{6})_1}{2^1 \cdot 1!}\;z^{-2} + \frac{(\tfrac{1}{6})_2 (\tfrac{5}{6})_2}{2^2 \cdot 2!}\;z^{-3} - \frac{(\tfrac{1}{6})_3 (\tfrac{5}{6})_3}{2^3 \cdot 3!}\;z^{-4} + \ldots

@@

\subsection{Going to the spatial domain}\label{spatial}
\subsubsection{A good try at $\zeta = 0$}
Let's try to find a function $\hat{K}_0$ with $K = \laplace_\zeta \hat{K}_0$, which is unique if it exists~\cite[Theorem~1.23]{laplace-tfm}. If a function $\hat{\varphi}$ satisfies the equation
\begin{equation}\label{eqn:spatial-mod-bessel}
\left[\big(\zeta^2 - 1\big) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] \hat{\varphi} = 0,
its Laplace transform $\varphi = \laplace_\zeta \hat{\varphi}$ satisfies the equation

>>>>

\usepackage{url}
\usepackage[hmargin=1.5in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor} %% for revisions

@@

\begin{document}
\maketitle
\section{The Laplace transform}
\subsection{Analytic version}
\subsubsection{Regularity and decay properties}\label{reg-decay}
Take two copies $\R$ and $\hat{\R}$ of the real line, with standard coordinates $z$ and $\zeta$ respectively. The Laplace transform in $\zeta$ turns a function $\hat{\varphi}$ on $\hat{\R}_{\zeta > 0}$ into a function $\laplace_\zeta \hat{\varphi}$ on $\R_{z > 0}$, defined by the integral
\[ \laplace_\zeta \hat{\varphi} = \int_0^\infty e^{-z \zeta}\,\hat{\varphi}\;d\zeta. \]
For $a \in [0, \infty]$, recall that recall that $O_{\zeta \to a}(g)$ is the space of functions $\varphi$ on $\hat{\R}_{\zeta > 0}$ with $|\varphi| \lesssim g$ in some neighborhood of $a$. A function is {\em subexponential} if it's in $O_{\zeta \to \infty}(e^{c\zeta})$ for all $c > 0$. Let $\mathcal{E}_\zeta$ be the space of subexponential functions on $\hat{\R}_{\zeta > 0}$ which are $L^1$ both locally and around $\zeta = 0$. If $\hat{\varphi}$ is in $\mathcal{E}_\zeta$, then $\varphi = \laplace_\zeta \hat{\varphi}$ is well-defined, and it extends to a holomorphic function on the right half-plane $\C_{\operatorname{Re}(z) > 0}$~\cite[\S 5.6]{diverg-resurg-i}. If $\hat{\varphi}$ is in $O_{\zeta \to 0}(1)$, then $\varphi$ is in $O_{z \to \infty}(z^{-1})$~\cite[equation~1.8]{laplace-tfm}.\footnote{The argument cited still works in our generality. For holomorphic $\hat{\varphi}$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textbf{(Sternin \& Shatalov)}.} More generally, if $\hat{\varphi}$ is in $O_{\zeta \to 0}(\zeta^{\alpha})$, with $\alpha > -1$, then $\varphi$ is in $O_{z \to \infty}\big(z^{-(\alpha + 1)}\big)$.
\subsubsection{Action on integral operators}\label{L-int-op}
When $\hat{\varphi} \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
\begin{equation}%%\label{id:L-mult}
\laplace_\zeta (\zeta^n \hat{\varphi}) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \hat{\varphi}.
\end{equation}
for all integers $n \ge 0$. You can also use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \hat{\varphi} \in \mathcal{E}_\zeta$ and
\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \hat{\varphi} = z^{-\lambda} \laplace_{\zeta, a} \hat{\varphi} \]
for all $\lambda \in (0, \infty)$.

@@

Now we have the results of Section~\ref{L-diff-op} for all functions in $\mathcal{E}_\zeta + \mathcal{P}_\zeta$. Identity~\ref{id:L-diff} is particularly simple when $\hat{\varphi}$ has a {\em fractional power singularity} at $\zeta = 0$. By this, I mean that $\hat{\varphi}$ can be written as $\hat{\varphi}_\text{frac} + \hat{\varphi}_\text{reg}$, where $\hat{\varphi}_\text{frac} \in \mathcal{P}_\zeta$ has only non-integer exponents, and the zeroth through $(n-1)$st derivatives of $\hat{\varphi}_\text{reg} \in \mathcal{E}_\zeta$ vanish at zero. Under this condition, all the initial value terms in the identity vanish, leaving
\[ \laplace_\zeta \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} = z^n \laplace_\zeta \hat{\varphi}. \]
\color{black}
\subsection{Change of coordinates}\label{translation}
Define a new coordinate $\zeta_a$ on $\hat{\R}$ so that $\zeta = a + \zeta_a$. From the calculation \textbf{[using variable starting point notation]}
\begin{align*}
\laplace_{\zeta, a} \hat{\varphi} & = \int_a^\infty e^{-z \zeta}\,\hat{\varphi}\;d\zeta \\
& = \int_0^\infty e^{-z(a + \zeta_a)}\,\hat{\varphi}\;d\zeta_a \\
& = e^{-az} \int_0^\infty e^{-z\zeta_a}\,\hat{\varphi}\;d\zeta_a \\
& = e^{-az} \laplace_{\zeta_a, 0} \hat{\varphi},
\end{align*}
we learn that
\[ \laplace_{\zeta_a, 0} \hat{\varphi} = e^{az} \laplace_{\zeta, a} \hat{\varphi}. \]

Define new coordinates $x$ and $\xi$ on $\R$ and $\hat{\R}$, respectively, so that $\zeta = b\xi$ and $z\,d\zeta = x\,d\xi$. Explicitly, $z = b^{-1}x$. From the calculation
\begin{align*}
\laplace_\zeta \hat{\varphi} & = \int_0^\infty e^{-z \zeta}\,\hat{\varphi}\;d\zeta \\
& = \int_0^\infty e^{-x\xi}\,\hat{\varphi}\;b\,d\xi \\
& = b \laplace_\xi \hat{\varphi},
\end{align*}
we learn that
\[ \laplace_\xi \hat{\varphi} = b^{-1} \laplace_\zeta \hat{\varphi}. \]
\section{Shifting integro-differential equations}\label{shifting}
Consider holomorphic functions on a simply connected open set that touches but doesn't contain $\zeta = 0$. A function is {\em regular} at $\zeta = 0$ if it extends holomorphically over that point. We'll say a function is {\em slight} at $\zeta = 0$ if it can be written as
\begin{equation}\label{eqn:slight-defn}
\zeta^{\alpha_1} f_1 + \ldots + \zeta^{\alpha_r} f_r + g
\end{equation}
where $f_1, \ldots, f_r$ are regular, $\alpha_1, \ldots, \alpha_r \in \R \smallsetminus \Z$, and $g, g', g'', \ldots$ go to zero at $\zeta = 0$.

Locally integrable slight functions play a special role in Laplace transform methods for linear differential equations. This is because differential equations in the frequency domain arise most naturally from integral equations in the spatial domain, but we'd like to work with differential equations in the spatial domain too. In the space of locally integrable slight functions, differential and integral equations enjoy their simplest equivalence.
\begin{prop}\label{prop:shifting}
When $\psi$ is slight and locally integrable at $\zeta = 0$,
\[ \left[ \sum_{k = 0}^n \big(\tfrac{\partial}{\partial \zeta}\big)^k \circ h_k + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
if and only if
\[ \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k + \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
where $h_n, \ldots, h_{-m}$ are regular functions.
\end{prop}
To prove this result, we'll need a little background.

@@

Multiplication by a regular function and differentiation with respect to $\zeta$ both preserve the space of slight functions. Integration from $\zeta = 0$ preserves the space of locally integrable slight functions. Thus, in general, integro-differential operators with regular coefficients send locally integrable slight functions to slight functions. Each basic operation has a simple effect on a slight function's order. Multiplication by $\zeta^n f$, where $f$ is regular and non-vanishing at $\zeta = 0$, adds $n$ to the order. Differentiation and integration add $-1$ and $1$, respectively.
\begin{proof}[Proof of Proposition~\ref{prop:shifting}]
The reverse implication holds without any special condition on $\psi$, because $\tfrac{\partial}{\partial \zeta}\;\fracderiv{-1}{\zeta}{0}$ acts as the identity on all differentiable functions.

@@

Integrating both sides of equation~\ref{eqn:diff-int-split}, we get
\[ \fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}\;\phi = -\left[ \fracderiv{-1}{\zeta}{0} \circ h_0 + \sum_{k = 1}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi. \]
Since $\fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}$ acts as the identity on functions that vanish at $\zeta = 0$, this simplifies to
\[ \phi = -\left[ \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi, \]
which rearranges to the second equation in the statement.
\end{proof}

@@

The method we'll demonstrate in Section~\ref{spatial} works for any differential equation
\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R(z^{-1}) \right] \varphi = 0, \]
where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function. Let's put equation~\ref{eqn:mod-bessel} in that form:
\begin{equation}\label{eqn:reg-mod-bessel}
\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \varphi = 0.
\end{equation}

\color{violet}
As we'll see in Section~\ref{asymp}, $K$ is in $O_{z \to \infty}(e^{-z})$. It'll be helpful to pull out the exponential decay factor and work instead with the function $\kappa$ defined by $K = e^{-z} \kappa$. Saying that $K$ satisfies equation~\ref{eqn:mod-bessel} is equivalent to saying that $\kappa$ satisfies the equation
\begin{equation}\label{eqn:shifted-mod-bessel}
\left[z^2 \big(\tfrac{\partial}{\partial z} + 1\big)^2 + z \big(\tfrac{\partial}{\partial z} + 1\big) - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] \varphi = 0.
\end{equation}
\color{black}
\subsection{Asymptotic analysis}
Equation~\ref{eqn:mod-bessel} has a regular singularity at $z = 0$ and an irregular singularity at $z = \infty$. From the general theory of such equations, we know that the space of trans-series solutions has a basis of trans-monomials
\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \} \]
where the $\series{W}_\alpha$ are formal power series in $z^{-1}$ with no constant term. From equations 10.40.2 and 10.17.1 of \cite{dlmf}, we learn that $K \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{1/2}\,\series{W}_1$, with
\begin{equation}\label{bessel-asymp}
\series{W}_1 = z^{-1} - \frac{(\tfrac{1}{6})_1 (\tfrac{5}{6})_1}{2^1 \cdot 1!}\;z^{-2} + \frac{(\tfrac{1}{6})_2 (\tfrac{5}{6})_2}{2^2 \cdot 2!}\;z^{-3} - \frac{(\tfrac{1}{6})_3 (\tfrac{5}{6})_3}{2^3 \cdot 3!}\;z^{-4} + \ldots
\end{equation}

The holomorphic analysis in Section~\ref{spatial} will give us holomorphic solutions
\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,W_\alpha \mid \alpha^2 - 1 = 0 \}, \]
which seem analogous to the trans-monomials above. Borel summation makes the analogy precise. We'll see in Section~\ref{bessel-regularity} that each $z^{\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{\tau_\alpha}\,\series{W}_\alpha$.
\subsection{Going to the spatial domain}\label{spatial}
\color{violet}
\subsubsection{A good try at $\zeta = 0$}
Let's try to find a function $\hat{K}_0$ with $K = \laplace_\zeta \hat{K}_0$, which is unique if it exists~\cite[Theorem~1.23]{laplace-tfm}. If a function $\hat{\varphi}$ satisfies the equation
\begin{equation}%%\label{eqn:spatial-mod-bessel}
\left[\big(\zeta^2 - 1\big) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] \hat{\varphi} = 0,
\end{equation}
its Laplace transform $\varphi = \laplace_\zeta \hat{\varphi}$ satisfies the equation
\begin{align*}
\left[\big({-\tfrac{\partial}{\partial z}}\big)^2 - 1\right] \Big(z^2 \varphi - \big[\hat{\varphi}\,z + \hat{\varphi}'\big]_{\zeta = 0}\Big) + 3\big({-\tfrac{\partial}{\partial z}}\big)\big[z\varphi - \hat{\varphi}\big]_{\zeta = 0} + \big[1 - \big(\tfrac{1}{3}\big)^2\big] \varphi & = 0 \\
\big(\tfrac{\partial}{\partial z}\big)^2 \big[z^2 \varphi\big] - \Big(z^2 \varphi - \big[\hat{\varphi}\,z + \hat{\varphi}'\big]_{\zeta = 0}\Big) - 3\big(\tfrac{\partial}{\partial z}\big)\big[z\varphi\big] + \big[1 - \big(\tfrac{1}{3}\big)^2\big] \varphi & = 0 \\
\Big[2 + 4z\tfrac{\partial}{\partial z} + z^2\big(\tfrac{\partial}{\partial z}\big)^2\Big]\varphi - \Big(z^2 \varphi - \big[\hat{\varphi}\,z + \hat{\varphi}'\big]_{\zeta = 0}\Big) - 3\Big[1 + z\tfrac{\partial}{\partial z}\Big]\varphi + \big[1 - \big(\tfrac{1}{3}\big)^2\big] \varphi & = 0,
\end{align*}
which simplifies to
\begin{equation}\label{eqn:inhomog-mod-bessel}
\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] \varphi = -\big[\hat{\varphi}\,z + \hat{\varphi}'\big]_{\zeta = 0}.
\end{equation}
Since we want $\laplace_\zeta \hat{K}_0$ to satisfy equation~\ref{eqn:mod-bessel}, which is the homogeneous version of equation~\ref{eqn:inhomog-mod-bessel}, we might guess that $\hat{K}_0$ is a solution of equation~\ref{eqn:spatial-mod-bessel} that vanishes through first order at $\zeta = 0$. Unfortunately, this would force $\hat{K}_0$ to be zero.
\color{black}
\subsubsection{The big idea}\label{big-idea}
We're going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\ref{eqn:reg-mod-bessel}. We'll succeed when $\alpha^2 - 1 = 0$, and we'll see that $K$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.

We can see from Section~\ref{L-int-op} that $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\ref{eqn:reg-mod-bessel} if and only if $v$ satisfies the integral equation
\begin{equation}\label{int-eq:spatial-mod-bessel}
\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] v = 0.
\end{equation}
It's tempting to differentiate both sides of this equation until we get
\begin{equation}\label{diff-eq:spatial-mod-bessel}
\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big[ \zeta^2 - 1 \big] - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v = 0,
\end{equation}
which is easier to solve. Unfortunately, a solution of equation~\ref{diff-eq:spatial-mod-bessel} won't satisfy equation~\ref{int-eq:spatial-mod-bessel} in general. However, as we learned in Section~\ref{shifting}, a solution of equation~\ref{diff-eq:spatial-mod-bessel} {\em will} satisfy equation~\ref{int-eq:spatial-mod-bessel} if it's slight and locally integrable at $\zeta = \alpha$.

This is great news, because equation~\ref{diff-eq:spatial-mod-bessel} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a slight solution at each regular singular point. We can see the regular singularities by moving the derivatives to the right:
\[ \left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v = 0. \]

In Sections \ref{pos-root}\,--\,\ref{neg-root}, we'll see this approach succeed. For each root $\alpha$, we'll find a solution $v_\alpha$ of equation~\ref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = \alpha$. This not only gives us solutions of equation~\ref{eqn:reg-mod-bessel}, but also tells us something about their asymptotics. Recall from Section~\ref{translation} that
\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha, \]
where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$. Observing that the order $\tau_\alpha$ of $v_\alpha$ is greater than $-1$, we can work out that $V_\alpha$ is in $o_{z \to \infty}(z^{-1-\tau_\alpha})$ \textbf{[recall definition of $o$]}. Now we can write our solution as
\[ e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
where $W_\alpha = z^{\tau_\alpha} V_\alpha$ is in $o_{z \to \infty}(z^{-1})$.
\color{Peru}
\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (\zeta - 1)(\zeta + 1) - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v & = 0
\color{Sienna}
\left[ \big[ 2 + 2(2\zeta) \tfrac{\partial}{\partial \zeta} + (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 \big] - \big[ 1 + \zeta \tfrac{\partial}{\partial \zeta} \big] - \big(\tfrac{1}{3}\big)^2 \right] v & = 0 \\
\left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0 \\
\left[ (\zeta - 1)(\zeta + 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0
%%In terms of the coordinate $\zeta_\alpha$ with $\zeta = \alpha + \zeta_\alpha$, this equation is written
%%\begin{equation}\label{eqn:centered-mod-bessel}
%%\[ \left[ \big[ \zeta_\alpha (\zeta_\alpha + 2\alpha) + \alpha^2 - 1 \big] + \fracderiv{-1}{\zeta_\alpha}{0} \circ \big[ \zeta_\alpha + \alpha \big] - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta_\alpha}{0} \right] w = 0. \]
%%\end{equation}
\subsubsection{Focus on $\zeta = 1$}\label{pos-root}
Let's find a solution of equation~\ref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = 1$. Define a new coordinate $\zeta_1$ on $\hat{\R}$ so that $\zeta = 1 + \zeta_1$. In this coordinate, equation~\ref{diff-eq:spatial-mod-bessel} looks like
\begin{equation}%%\label{diff-eq:spatial-mod-bessel-pos}
\left[\zeta_1(2 + \zeta_1) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + 3(1 + \zeta_1) \tfrac{\partial}{\partial \zeta_1} + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0.

@@

With another change of coordinate, given by $\zeta_1 = -2\xi_1$, we can rewrite equation~\ref{diff-eq:spatial-mod-bessel} as the hypergeometric equation
\begin{equation}\label{diff-eq:hypergeom-pos}
\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + 3(\tfrac{1}{2} - \xi_1) \tfrac{\partial}{\partial \xi_1} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0.

@@

Looking through the twenty-four expressions for Kummer's six solutions, we find one \cite[formula~15.10.12]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 0$:
\begin{alignat*}{2}
v_1 &=\;& \hphantom{-i\sqrt{2}}\,\xi_1^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi_1\big) \\
&=\;& -i\sqrt{2}\,\zeta_1^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big)
\end{alignat*}
From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\ref{eqn:mod-bessel}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$. Observing that $v_1$ has order $-1/2$, we learn that $V_1 = z^{1/2} W_1$ for some $W_1 \in o_{z \to \infty}(z^{-1})$.
\subsubsection{Focus on $\zeta = -1$}\label{neg-root}
Let's find a solution of equation~\ref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = -1$. In the rescaled coordinate from Section~\ref{pos-root}, this is the point $\xi_1 = 1$. Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 1$:
\begin{alignat*}{2}
